%
%  Main file for James Till Matta's dissertation
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[final,numrefs,sort&compress]{nddiss2e}

\usepackage{graphicx}   % need for figures
\usepackage{dcolumn}    % use to align table columns on decimal point
\usepackage{epstopdf}   % allows use of eps figures
\epstopdfsetup{update}  % only regenerate pdf files when eps file is newer
%\usepackage{xstring}    % for \IfEqCase
\usepackage{amssymb}    % for a few symbols
\usepackage{multirow}   % for the multirow command
\usepackage{booktabs}   % for nice lines in tables
\usepackage{longtable}  % for super long tables (I'm looking at you calibration parameter sets)
\usepackage{xfrac}      % for sfrac
\usepackage{braket}     % for good looking bra-ket notation
\usepackage{mathrsfs}   % for math script symbols like those used for rotation operators
\usepackage{ dsfont }   % for fancy integer symbols
\usepackage{ragged2e}
% % % % % % % % % % % % % % % % % %
% Define a few commands for conveniences sake
\newcommand{\gr}{$\gamma$ ray}
\newcommand{\pr}{$^{135}$Pr}
\newcommand{\uvec}[1]{\boldsymbol{\hat{\textbf{#1}}}}


\begin{document}

\frontmatter 
\title{EXOTIC NUCLEAR EXCITATIONS:\\
THE TRANSVERSE WOBBLING MODE IN \pr{}}
\author{James Till Matta}
\work{Dissertation}
\degaward{Doctor of Philosophy}
\advisor{Umesh Garg}
\department{Physics}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Front stuff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% You must either set the copyright information or put your work in the public domain.
\copyrightholder{James Till Matta} % See template or documentation for
\copyrightyear{2015}           % other copyright options.
\makecopyright

% An abstract is optional for a mster's thesis, and required for a doctoral dissertation.
\begin{abstract}
The exotic collective excitation transverse wobbling has been investigated in the nucleus, \pr{}. A pair of zero and one-phonon wobbling bands has been observed. The nature of these wobbling bands was confirmed by the $\Delta{}I=1, E2$ nature of the $n_w=1\rightarrow n_w=0$ interband transitions making \pr{} the first nucleus observed to exhibit wobbling behavior other than five nuclei in the $A\sim{}160$. Additionally, a possible two-phonon wobbling band has been observed and its nature has been partially confirmed by measuring the $\Delta{}I=1, E2$ nature of the $n_w=2\rightarrow n_w=1$ interband transitions. The theory of transverse wobbling was proposed to explain contradictions in the wobbling energy predicted by previous quasiparticle plus triaxial rotor calculations; this theory has been confirmed. In this model, the quasiparticle aligns with an axis perpendicular to the axis with maximal moment of inertia (in contrast to previous theories, which aligned the quasiparticle with the axis with maximum moment of inertia). With this modification the fall in the energy of the wobbling phonon, observed in experiment, is now correctly predicted by theory. This confirmation of theory suggests a reevaluation of the previously discovered wobbling nuclei in the $A\sim{}160$ region in the framework of transverse wobbling as well.
\end{abstract}

% A dedication is optional.
\renewcommand{\dedicationname}{DEDICATION:}

\begin{dedication}
	To my fianc\'e Tina.\\\&\\To my parents, James and Margaret.\\
	In loving recognition of their support.
\end{dedication}

% These are required, and must be in this order.
\tableofcontents
\listoffigures
\listoftables

\begin{acknowledge}
In the long and difficult period I have been a student at Notre Dame many individuals have assisted me, giving their time, scientific guidance, and emotional support, without them I would have failed in this task and I remain indebted to them. I would like to sincerely thank every contributor to this work; thank you.

Foremost, I would like to offer my most profound thanks to Dr. Umesh Garg, my research advisor here at Notre Dame. I am grateful for his introducing me to the world of nuclear physics. Without his guidance, none of this would have been possible. Without his understanding, I would not have succeeded. His push to constantly improve my analysis and test \emph{why} something happens rather than simply accept it has had a major impact on me and my way of thinking. Without his patience, comments, and advice, this manuscript would be much poorer. I am profoundly gratefule for his advice and assistance.

I would like to thank my committee, past and present, for their assistance and advice. To Dr. James Kolata and Dr. Collin Jessop, I would like to apologize for the scheduling problems that prevented your participation in the defense, and accept my sincere thanks for steering my research and giving good advice on post-doctorate positions. Dr. Stefan Frauendorf's assistance has been invaluable in helping me understand the theory behind this work; I remain in your debt. To Dr. Anna Simon and Dr. Bruce Bunker, your willingness to become members of my committee on short notice has enabled me to complete this effort. You have my deepest thanks and gratitude.

I would like to extend thanks to Ms. Weichaun Li, Dr. Friedrich D\"onau, and Dr. Stefan Frauendorf for their excellent theoretical work. It has made a more complete interpretation and understanding of the data possible.

To Dr. Rajarshi Raut I extend my humble thanks. His patience with my many questions was genuinely appreciated. Equally appreciated was his guidance in a land that was new and different to me.

I would like to thank Dr. Robert V.F. Janssens, without his assistance, guidance, and patience in early conferences, I would have been lost.

What skills I have learned in the analysis and interpretation of gamma-ray coincidence data, I owe to Dr. Somsundar Mukhopadhyay, Dr. Shaofei Zhu, Dr. Xiaofeng Wang, and Dr. Daryl Hartley. The codes they provided and the skills they taught are a great boon to me, and I am thankful for their patience in passing them on.

I would like to deeply thank Dr. Akaa D. Ayangeakaa and Dr. Darshana Patel. They were my year-mates and friends while here. Their counsel has assisted me in maturing and their scientific discussions have enlightened. Further, their camaraderie has made for pleasant times while at Notre Dame. I thank you both from the bottom of my heart.

I would like to thank the other scientists who collaborated on the work presented in this dissertation Dr. Rudrajyoti Palit, Dr. Sudipta Saha, Dr. Jasmine Sethi, Dr. Tarkeshwar Trivedi, Dr. Sandeep S Ghugre, Dr. Ajit K Sinha, Dr. Michael P. Carpenter, Dr. Torben Lauritsen, Dr. Darek Seweryniak, Dr. Filip Kondev, Dr. Christopher J. Chiara, Ms. D. Vijaya Lakshmi,  Dr. P.V. Madhusudhana Rao, Dr. M. Kumar Raju, Dr. Sujit Tandel, and Dr. Sudipta Ray. Without their support in sitting shifts and dealing with the data, this task would have been Herculean at best and impossible, more realistically.

I wish to thank the staff of the ATLAS facility and the TIFR-BARC Pelletron facility. Without their diligent troubleshooting and operation of the machines, this journey could not have started, let alone finished.

If in my haste, I have omitted anyone I offer my sincere apology. So many have been of assistance in this quest; I am profoundly moved by their generosity of spirit.

I would like to thank my parents Margaret and James. Without their anecdotes of their own time in graduate school, I would be much less sane. Without their copy editing, this document would be poorer, and rife with grammatical errors.

Last but most important, I would like to thank my fianc\'{e} Tina without her, love, understanding, and emotional support I would have fallen from this path long ago.

This work has been supported in part by the U.S. National Science Foundation [Grants No. PHY-0758100 (UND), PHY-1068192 (UND), PHY-1419765(UND), and No. PHY-1203100 (USNA)]; by the APS-IUSSTF Physics Student and Post-doc Visitation Program; by the U.S. Department of Energy, Office of Science, Office of Nuclear  Physics,  under  Contracts  No.  DE-AC02-06CH11357 (ANL), No. DE-FG02-95ER40934 (UND), and No. DE-FG02-94ER40834 (UMCP); and by the Department of Science and Technology, Government of India (Grants No. IR/S2/PF-03/2003-II and No. IR/S2/PF-03/2003-III). This research used resources of ANL’s ATLAS facility, which is a DOE Office of Science User Facility.
\end{acknowledge}

% A symbols section is optional.
\begin{symbols}
\sym{c}{Speed of light in vacuum}
\sym{\hbar}{Reduced Planck Constant}
\sym{FWHM}{Full Width at Half Maximum}
\sym{Z}{Number of protons within a nucleus}
\sym{A}{Number of nucleons within a nucleus}
\sym{pnA}{particle nanoamps ($6.24151\times{}10^9$ particles/second)}
\end{symbols}

\mainmatter
%
% An unnumbered chapter (features)
%
%\unnumchapter{FEATURES OF FORMATTING IN THIS EXAMPLE FILE}
% The \unnumchapter command allows you to include an unnumbered chapter as part of
% the main text before Chapter 1. It will appear in your table of contents, and you
% should have at most one such chapter (although nothing in the class file will
% prevent you from creating more).

%
% Chapter 1 - General Introduction
%
\include{cmn_chaps/chapter_01_introduction}

%
% Chapter 2 - Nuclear Models
%
\include{pr_chaps/chapter_02_nuclear_models}

%
% Chapter 3 - 135Pr exp methods
%
\include{pr_chaps/chapter_03_pr_exp_methods}

%
% Chapter 4 - Transverse wobbling in 135Pr
%
\include{pr_chaps/chapter_04_transverse_wobbling}

%
% Chapter 5 - wobbing discussion
%
\include{pr_chaps/chapter_05_wobbling_discussion}

%
% Appendix (optional)
%

\appendix

%
% Appendix on GS Rings and Detectors
%
\include{appendices/appendix_gs_ring_and_det}

%
% Appendix on INGA Rings and Detectors
%
\include{appendices/appendix_inga_ring_and_det}

%
% Appendix on Neg Parity Level Scheme
%
\include{appendices/appendix_neg_parity_tables}

%
% Appendix on Full Level Scheme
%
%\include{appendices/appendix_full}

%
% Back stuff
%

% % comment out the following three lines
% if using chapter-wise bibliography

\backmatter
\bibliographystyle{nddiss2enoarticletitles} % The standard abbrvnat style should be acceptable. Also provided with both the advanced and standard
%\bibliographystyle{test}
\bibliography{dissertation}       % distributions are nddiss2e and nddiss2enoarticletitles style options.

\end{document}
